AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-13 chapters/05-discussion.tex
Add bus discussion

% Finally, it was observed during all tests that the loss of a frame could be
% reported twice in the reception statistics: the last decoded frame number is
% only changed when a valid frame is parsed, and the frame sequence number is
% discarded if the frame contains too many erroneous bytes and cannot be
% corrected. While this avoid tracking corrupt frame sequence numbers in the
% decoder, it means that a corrupt frame will not be registered in the sequence,
% and the decoder will report a dropped frame when

\subsection{Payload Bus}

The payload bus

@@

Finally, table \ref{tab:ditl-health} shows that even though the data bus
performed well overall, both test payloads were marked as unresponsive in
nearly \SI{10}{\percent} of the system health packets transmitted by the
platform. The source of the problem could not be identified due to the lack of
time and the difficulty of debugging this subsystem in particular: the
Wemos D1 development board that was used as the \acrlong{obc} does not provide
useful printing devices that could have been used to send log messages.

>>>>

\subsection{Payload Bus}
\label{ssec:discussion-bus}

The payload data bus worked well overall, even though payloads failed to
respond in certain occurrences. Due to the absence of debugging facilities on
the Wemos D1 development board and lack of time, the root cause of this issue
could not be successfully identified. One possibility is the difference in
logical levels between the \acrlong{obc} (\SI{3.3}{\volt}) and the test
payloads (\SI{5.0}{\volt}). While in practice both side were able to detect
logical highs and lows, it is possible that performance could be improved by
using a voltage regulator on the data and clock lines. Additionally, the test
payloads were written using the Arduino libraries, which provide an easy-to-use
API to interact with AVR-based boards, but include a lot of overhead. It is
possible that some length interrupt service routines or I/O actions were
delaying the payloads' responses to \acrshort{i2c} requests, causing the
\acrshort{obc} to flag them as unresponsive.

Of all the systems designed for this project, the payload bus was the most
simple – it relies heavily on \acrshort{i2c}, an existing protocol – but also
the one that was the most complex to test thoroughly, and the one that would
require the most additional testing to be approved before a real test mission.

@@

It is important to note that the amount of erroneous data received was lower
than that reported by the decoder/parser, due to software design. 256 bytes are
added to the erroneous data count when a frame has too many errors to be
error-corrected, or when frames are skipped – the current frame sequence number
is higher than expected. When a corrupt frame is detected, the last decoded
sequence number is not changed to avoid overwriting it with a potentially
corrupted value. Because of this, the next valid frame to be detected will
also cause a dropped frame to be reported, even though the corrupt's frame
256 bytes have already been recorded.

Finally, table \ref{tab:ditl-health} shows that even though the data bus
performed well overall, both test payloads were marked as unresponsive in
nearly \SI{10}{\percent}, which can be considered high. As discussed in section
\ref{ssec:discussion-bus}, a single root cause could not be identified for this
particular issue, and more testing would be required.
